%-------------------------
% Resume - Sundram Yadav
% Compile: pdflatex resume.tex
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{multirow}
\input{glyphtounicode}

\usepackage[default]{lato}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}

\titleformat{\section}
  {\vspace{4pt}\scshape\raggedright\small\bfseries}{}{0em}{}[\vspace{-2pt}\color{black}\rule{\columnwidth}{0.4pt}]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\newcommand{\project}[2]{
  \noindent\textbf{#1}\hfill\footnotesize#2\par
}

\newcommand{\skill}[2]{\noindent\textbf{#1:} #2\par}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\setlist{leftmargin=8pt, nosep, before={\vspace{2pt}}}

\pdfgentounicode=1

\begin{document}

%----------HEADING----------%
\begin{center}
  {\LARGE\bfseries Sundram Yadav}\\[2pt]
  {\footnotesize
  \faPhone\ +91-9015276758 \quad
  \faEnvelope\ \href{mailto:osamabinladenfromindia@gmail.com}{osamabinladenfromindia@gmail.com} \quad
  \faGithub\ \href{https://github.com/SirYadav1}{SirYadav1}
  }
\end{center}

%----------TWO COLUMN LAYOUT----------%
\begin{multicols}{2}

%-----------LEFT COLUMN-----------%

\section{Summary}
Backend developer building tools for security, automation, and web. 510+ commits across 15+ projects. Linux enthusiast.

\section{Skills}
\skill{Languages}{Python, PHP, Go, JavaScript, TypeScript, Kotlin, Bash}
\skill{Backend}{Node.js, Express, NestJS, REST, GraphQL}
\skill{Frontend}{Vue.js, React}
\skill{DB}{MySQL, SQLite, TypeORM}
\skill{Infra}{Linux, Docker, Nginx, Git, WebSocket}
\skill{Security}{Network Scanning, Burp Suite, Nmap, Bug Bounty}
\skill{CS}{DSA, OS, Networks, Multithreading, System Design}

\section{Experience}

\noindent\textbf{Code Audit \& Refactoring}\hfill\footnotesize 2026\par
\footnotesize Audited and cleaned full-stack repos (Zyphron Dash, IGNOU Bot) -- scrubbed git history, removed secrets, added LICENSE, restructured code, prepared for public release.

\vspace{3pt}
\noindent\textbf{Open Source Developer}\hfill\footnotesize 2023--Present\par
\footnotesize Built 15+ projects from scratch. Focused on security tools, Telegram bots, and web apps.

\vspace{3pt}
\noindent\textbf{Security Researcher}\hfill\footnotesize 2024--Present\par
\footnotesize Bug bounty hunting. Vulnerability discovery and responsible disclosure.

\section{Education}
\noindent\textbf{BCA}\hfill\footnotesize 2024--Present\par
\footnotesize SPU University, Himachal -- 3rd Sem\par
\vspace{3pt}
\noindent\textbf{12th (Arts) -- 75.6\%}\hfill\footnotesize 2023\par
\footnotesize Govt. Sr. Sec. Boy School, Himachal

%-----------RIGHT COLUMN-----------%
\columnbreak

\section{Projects}

\project{AdwanceSNI 2.0}{Python}
\footnotesize Multithreaded network recon suite -- subdomain discovery, host scanning, IP tools. 75 commits, 24 stars, 9 forks.
\vspace{4pt}

\project{Zyphron Free Dash}{Vue + NestJS}
\footnotesize Full-stack hosting platform with credit economy, Pterodactyl integration, 130+ API endpoints.
\vspace{4pt}

\project{AdwanceSNI}{Python}
\footnotesize SNI finding tool. 35 commits, 11 stars, 3 forks.
\vspace{4pt}

\project{IGNOU Grade Card Bot}{Python}
\footnotesize Telegram bot scraping IGNOU portals for assignment status and grade card data.
\vspace{4pt}

\project{FlashScan Go}{Go}
\footnotesize High-performance security scanner with parallel scanning.
\vspace{4pt}

\project{API Rate Limiter}{Node.js}
\footnotesize Real-time API monitoring dashboard with WebSocket, SQLite, Docker.
\vspace{4pt}

\project{TG Chat Fetch}{Python}
\footnotesize Telegram chat archiver with multi-target backup and auto-resume.
\vspace{4pt}

\project{Insta Downloader}{PHP}
\footnotesize Telegram bot for Instagram video downloads. 3 stars, 1 fork.
\vspace{4pt}

\project{Domain Splitter}{Shell}
\footnotesize Splits large domain lists into manageable files. 3 stars.
\vspace{4pt}

\project{youtube-discord-rpc}{Python}
\footnotesize Browser ext + Python server syncing YouTube to Discord rich presence.

\section{Contributions}
\project{AirBeats}{Kotlin}
\footnotesize Android music player. Contributed Google Sign-In, onboarding flow, crash fixes. 100+ commits.

\section{Achievements}
\footnotesize
\begin{itemize}
  \item 510+ commits, 40+ stars across 15+ repos
  \item AdwanceSNI 2.0: 24 stars, 9 forks
  \item Bug bounty -- responsible disclosures
\end{itemize}

\end{multicols}

\end{document}
